Fast Hyper-Parameter Selection for Graph Kernels via Subsampling and\\Multiple Kernel Learning

### 2016-11-26 paper.tex
modifiche di Fabio

\section{Introduction}
In different real-world domains, it may be easy to encode examples in a structured form. For example, in chemoinformatics there is a well known graph representation of the secondary structures of chemical compounds. Moreover, images can easily be represented as graph after segmentation, where adjacent objects (or regions) are linked.
In these cases, derive a vectorial representation for the data may be a time-consuming task, where information from  domain experts is needed, and information loss is, in general, unavoidable.
Another option is to deal directly with examples represented in a structured form.
In this case, specific machine learning techniques have to be adopted.
Kernel methods are one option, where it suffices to adopt a kernel function defined for data type under consideration. Then, standard (kernelized) learning algorithms (e.g. SVM) can be adopted.

With kernel methods, a user has usually to deal with a number of hyper-parameters to fix at hand. The optimization of these hyper-parameters can strongly affect the predictive performance of the method.
Usually, these parameters are: (i) the choice of the kernel to adopt; (ii) the hyper-parameters of the selected kernel; (iii) the hyper-parameters of the learning algorithm.
A commonly adopted and simple approach to hyper-parameters optimization is to fix a-priori some possible values for each parameter (the combinations of these parameters are referred to as \textit{parameters grid}).
Then, the learning algorithm is trained for each possible parameters combination, and its performances are evaluated. This approach is commonly referred to as grid-search.

>>>>

\section{Introduction}
In different real-world domains, it may be easy to encode examples in a structured form. For example, in chemoinformatics there is a well known graph representation of the secondary structures of chemical compounds. Moreover, images can easily be represented as graph after segmentation, where adjacent objects (or regions) are linked.
In these cases, deriving a vectorial representation for the data may be a time-consuming task, where information from  domain experts is needed, and information loss is, in general, unavoidable.
Another option is to deal directly with examples represented in a structured form.
In this case, specific machine learning techniques have to be adopted.
Kernel methods are one option, where it suffices to adopt a kernel function defined for data type under consideration. Then, standard (kernelized) learning algorithms (e.g. SVM) can be adopted.

With kernel methods, a user has usually to deal with several of hyper-parameters to fix manually. The optimization of these hyper-parameters can strongly affect the predictive performance of the method.
Usually, these parameters are: (i) the choice of the kernel to adopt; (ii) the hyper-parameters of the selected kernel; (iii) the hyper-parameters of the learning algorithm.
A commonly adopted and simple approach to hyper-parameters optimization is to fix a-priori some possible values for each parameter (the combinations of these parameters are referred to as \textit{parameters grid}).
Then, the learning algorithm is trained for each possible parameters combination, and its performances are evaluated. This approach is commonly referred to as grid-search.
